---
title: "DosePredict Report"
output: 
  html_document:
    toc: true
    theme: united
params:
  AuthorParam: NA
  CompoundParam: NA
  Commentsenterd: NA
  Modelname: NA
  ModelParameters: NA
  DosingParams: NA
  SafetyParams: NA
  EfficacyParams: NA
  NCALimitsParams: NA
  NCAtable1: NA
  Efftable1: NA
  SAFtable1: NA
  Pkplot: NA
  plotallNCA1: NA
  plotSAFNCA1: NA
  plotEFF1: NA
  plotEFF2: NA
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
</style> 


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```


__Date__: `r format(Sys.time(), ' %B %d, %Y')`  
__Author__: `r params$AuthorParam`   
__Compound ID__: `r params$CompoundParam`  
__Run Comments__: `r params$Commentsenterd`

# Simulation Inputs:

## 1- Pharmacokinetic Input:
The __Pharmacokinetic model__ used is `r params$Modelname`.  
The __Pharmacokinetic Parameters__ used in the simulations are:    
```{r Pk Param, echo=F, warning=F}
# The `params` object is available in the document.
kable(params$ModelParameters)

```

## 2- Dosing Input:  
The __dosing infromation__ evaluated in the simulations are:  
```{r Dosing, echo=F, warning=F}
# The `params` object is available in the document.
kable(params$DosingParams)

```


## 3- Safety and Efficacy Targets:   
The __Safety limits__ used in the simulations are:  
```{r SafetyParams, echo=F, warning=F}
# The `params` object is available in the document.
kable(params$SafetyParams)

```

And the __target efficacy concentration limit__ used is:  

```{r Efficacy targets, echo=F, warning=F}
# The `params` object is available in the document.
kable(params$EfficacyParams)

```

## 4- NCA Input:   

The NCA calculations results are:    

```{r NCA, echo=F, warning=F}
# The `params` object is available in the document.

kable(params$NCAtable1,  digits=4)

```

# Results:

## 1- Safety Calculations: 

The safety calculations in relation to safety targets  are:  
```{r saf table, echo=F, warning=F}
# The `params` object is available in the document.

kable(params$SAFtable1,  digits=4)

```


## 2- Efficacy Calculations:

The efficacy calculations in relation to efficacy targets  are: 

```{r Eff table, echo=F, warning=F}
# The `params` object is available in the document.

kable(params$Efftable1,  digits=4)

```

## 3- NCA Calculations:

The NCA calculations were done within the below __NCA time frame__:  

```{r NCA time fram, echo=F, warning=F}
# The `params` object is available in the document.
kable(params$NCALimitsParams)

```



# Plots:

## 1- Simulation Plot:

```{r , message = FALSE, echo = FALSE, warning=FALSE}
# The `params` object is available in the document.
ggplotly(params$Pkplot,session="knitr")
    
```

## 2- NCA Histograms:

```{r , message = FALSE, echo = FALSE, warning=FALSE}
# The `params` object is available in the document.
print(params$plotallNCA1)
#ggplotly(params$plotallNCA1,session="knitr")

```

## 3- Safety Histogram:

```{r , message = FALSE, echo = FALSE, warning=FALSE}
# The `params` object is available in the document.
#print(params$plotallNCA1)
ggplotly(params$plotSAFNCA1,session="knitr")

```

## 4- Efficacy Histograms:

```{r , message = FALSE, echo = FALSE, warning=FALSE}
# The `params` object is available in the document.
#print(params$plotallNCA1)
ggplotly(params$plotEFF1,session="knitr")

```
```{r , message = FALSE, echo = FALSE, warning=FALSE}
# The `params` object is available in the document.
#print(params$plotallNCA1)
ggplotly(params$plotEFF2,session="knitr")

```


END of REPORT
